\chapter{Extensions around the ArduPilot Framework}

Now that everything is set up.
The different functionalities required for this project could be implemented.

One part was the handling of multi vehicles.
ROS add to be configured on the different machine to be able to run synchronized.

Another part was setting up the simulation.
It is interesting because it allows us to test the firmware and the code of the drone on the computer.
It allows for a fast test because you do not have to set up the hardware every time.
And you minimize risk because you cannot break your computer with it.

Another part was the interfacing with the motion capture system at the lab.
There was not enough time to implement it.

The autopilot had to be configured to use the Vicon data in the EKF.

\section{Multi-vehicle}

\subsection{ROS Setup}
\subsubsection{Setup on computer}
\begin{enumerate}
    \item Run on your computer

          \begin{minted}{bash}
    # Install the ros package mavros
    sudo apt install ros-<distribution>-mavros
    # Setup tell ROS what is the IP address of this computer
    # (change 192.168.1.100 by your computer IP address if you use a different one)
    echo "export ROS_IP=192.168.1.100" >> ~/.bashrc
    # Apply modification
    source ~/.bashrc
                    \end{minted}
    \item \texttt{printenv|grep ROS} prints ROS environment variables
    \item \texttt{echo \$ROS\_IP}, to check if the address has been updated
\end{enumerate}

\subsubsection{ROS Setup on Raspberry Pi}

The Raspberry Pi uses ROS with a \texttt{MAVROS} node on each one. And they are connected by wifi to a router that is also connected to a computer running \texttt{roscore}.
\begin{enumerate}
    \item Run these commands after ssh into the Raspberry Pi

          \begin{minted}{bash}
# Setup ROS at the startup of the Raspberry Pi
echo "source /opt/ros/kinetic/setup.bash" >> ~/.bashrc
# Install GeographicLib needed for mavros
sudo /opt/ros/kinetic/lib/mavros/install_geographiclib_datasets.sh
# Setup where roscore is running (change 192.168.1.100 by your computer IP address if you use a different one)
echo "export ROS_MASTER_URI=http://192.168.1.100:11311" >> ~/.bashrc
# Setup tell ROS what is the IP address of this Raspberry Pi
echo "export ROS_IP=192.168.1.1<xx>" >> ~/.bashrc
# Apply modification
source ~/.bashrc
                    \end{minted}
    \item \texttt{printenv|grep ROS}: check \texttt{ROS\_MASTER\_URI} and \texttt{ROS\_IP}
\end{enumerate}

\subsubsection{ArduPilot Setup on Raspberry Pi}
\begin{enumerate}
    \item Run \texttt{sudo nano /etc/default/arducopter}, to use the telemetry the telemetry locally for \texttt{MAVROS}.

          \begin{minted}{bash}
# Change this line
TELEM1="-A udp:192.168.1.100:14550"
# by this line
TELEM1="-A udp:127.0.0.1:14650" #same for all Raspberry Pies
# Save the change
          \end{minted}

    \item Run \texttt{sudo systemctl restart arducopter} to apply the change and restart arducopter.
    \item Go into the \texttt{MAVROS} folder with \texttt{roscd mavros}.
    \item Go into the launch folder \texttt{launch} with \texttt{cd launch}.
    \item \texttt{sudo nano node.launch} and \texttt{sudo nano apm.launch}.
\end{enumerate}

\begin{minted}{bash}
# In node.launch replace mavros
<node pkg="mavros" type="mavros_node" name="mavros"
# by mavros<xx> (e.g. mavros01) the number of the Raspberry Pi
<node pkg="mavros" type="mavros_node" name="mavros<xx>"
# This will change the name of the mavros node to mavros<xx> to avoid conflict.

# In apm.launch replace
<arg name="fcu_url" default="/dev/ttyACM0:57600" />
<arg name="gcs_url" default="" />
# by this
<arg name="fcu_url" default="udp://:14650@" />
<arg name="gcs_url" default="udp://:14551@192.168.1.100:140<xx>" />
# the fcu_url is the url of the Raspberry Pi local telemetry
# the gcs_url is the url of the computer for the Ground Control Station
\end{minted}

To execute the launch file at the Raspberry Pi startup. A service called \texttt{mavros} has been created.
For more information on service check \ref{services}.

\begin{enumerate}
    \item \texttt{cd /lib/systemd/system}
    \item \texttt{sudo nano mavros.service}
          \begin{minted}{bash}
[Unit]
Description=mavros

[Service]
Type=simple
ExecStart=/bin/bash -c "source /opt/ros/kinetic/setup.bash;\
export ROS_MASTER_URI=http://192.168.1.100:11311;\
export ROS_IP=192.168.1.1<xx>;\
/usr/bin/python /opt/ros/kinetic/bin/roslaunch mavros apm.launch"
Restart=on-failure

[Install]
WantedBy=multi-user.target
                    \end{minted}
    \item \texttt{sudo systemctl daemon-reload}
    \item \texttt{sudo systemctl start mavros}
\end{enumerate}

\subsubsection{Texting on the computer the ROS configuration}
\begin{enumerate}
    \item Launch \texttt{roscore} on your computer
    \item Reboot Raspberry Pi \texttt{ssh pi@192.168.1.1<xx> sudo systemctl restart mavros}
    \item Launch QGroundControl
    \item \texttt{rosnode list} should show you

          \begin{minted}{bash}
/mavros<xx>
/rosout
          \end{minted}
    \item \texttt{rosservice call /mavros/set\_stream\_rate 0 10 1}
    \item \texttt{rostopic echo /mavros/imu/data}
\end{enumerate}

\subsection{ROS nodes}
ROS is now setup and all Raspberry Pi and the ground station computer.
It is now explained which nodes are used for the future of this project.
It is a proposition of implementation.

\subsubsection{Node list}

The following nodes are the ones that are already implemented.

\begin{description}
    \item[vicon\_bridge] get the absolute position of the drone from the VICON system.
          It runs on the ground station computer.
    \item[mavros] is a bridge between the ArduPilot firmware and ROS.
          The drone can be controlled from this node.
\end{description}

The following nodes are the one that has to be implemented

\begin{description}
    \item[vicon2mavros] transmit the data from \texttt{vicon\_bridge} to \texttt{mavros}.
          Then \texttt{mavros} send the absolute position to the EKF.
    \item[drone2drone] transmit data from the drone and Vicon from drones to drones.
          The data transmitted can be customized.
\end{description}

There is one \texttt{mavros}, \texttt{vicon2mavros} and \texttt{drone2drone}
node for each drone. To avoid conflict, \texttt{<xx>} is added to their name (e.g. mavros01, drone2drone42).
All these nodes can run on the ground station control, or one can run on each drone.

\subsection{Deployment}
As this project uses multiple drones, many things need to be done \texttt{xx} times (\texttt{xx} being the number of drones), but it does have to be done manually.
Scripts can be written to automate most of the code deployment.

These are some ideas for this project.
\begin{description}
  \item[rsync] can be used to synchronize files via ssh
  \item[cross-compiling] on your computer and then send the binary to the Raspberry Pi \cite{hackaday_cross_compiling}.
  \item[bash scripts] to avoid typing all the commands in the terminal. Checking if the commands succeed is important to ensure nothing wrong happened. \cite{ryanstutorials_bash_scripting}
\end{description}

\section{Simulation}

\subsection{Installation of SITL Software}
Ubuntu 18.04 is used.

These instructions have been used to set up the SITL simulator \cite{ardupilot_sitl}.

\begin{minted}{bash}
# Setting up the Build Environment on Linux
# Clone ArduPilot repository with Copter 3.6 version
cd ~
git clone -b Copter-3.6 https://github.com/ArduPilot/ardupilot
cd ardupilot
git submodule update --init --recursive
    # Install some required packages
Tools/environment_install/install-prereqs-ubuntu.sh -y
    # Reload the path (log-out and log-in to make permanent)
. ~/.profile

# Start SITL simulator
cd ~/ardupilot/ArduCopter
sim_vehicle.py --console --map
\end{minted}

Install the full desktop version of ROS Melodic using this link \cite{ros_install}.

Gazebo is installed with it.

\begin{minted}{bash}
# Try launching gazebo in the terminal
gazebo
            \end{minted}

If there is an error in the terminal containing \texttt{api.ignitionfuel.org}.

Replace inside
\begin{verbatim}
~/.ignition/fuel/config.yaml

url: https://api.ignitionfuel.org
by
url: https://api.ignitionrobotics.org
\end{verbatim}

Then, the ArduPilot for Gazebo Simulator is installed
\begin{minted}{bash}
# Installation steps
cd ~
git clone https://github.com/khancyr/ardupilot_gazebo
cd ardupilot_gazebo
mkdir build
cd build
cmake ..
make -j4
sudo make install

# Launch Gazebo with
gazebo --verbose worlds/iris_arducopter_runway.world

# and in another terminal execute
cd ~/ardupilot/ArduCopter
../Tools/autotest/sim_vehicle.py -f gazebo-iris --console --map
\end{minted}

Installation of MAVROS \cite{ardupilot_install_mavros}
\begin{minted}{bash}
sudo apt-get install ros-melodic-mavros ros-melodic-mavros-extras

# The following command is cut in two lines as it did not fit on the page.
wget https://raw.githubusercontent.com/mavlink/mavros/master/mavros\
/scripts/install_geographiclib_datasets.sh
chmod a+x install_geographiclib_datasets.sh

# If this command return This script require root privileges!
./install_geographiclib_datasets.sh
# Run with sudo
sudo ./install_geographiclib_datasets.sh
# Then delete the script
rm install_geographiclib_datasets.sh

# The following command is cut in two lines as it did not fit on the page.
sudo apt-get install ros-melodic-rqt ros-melodic-rqt-common-plugins\
ros-melodic-rqt-robot-plugins python-catkin-tools
\end{minted}

Connect ArduPilot to ROS \cite{ardupilot_ros_sitl}
\begin{minted}{bash}
# Create ArduPilot ROS workspace
cd ~
mkdir -p ardupilot_ws/src
cd ardupilot_ws
catkin init
cd src

# Copy apm.launch from MAVROS
cd ~/ardupilot_ws
mkdir launch
cd launch
roscp mavros apm.launch apm.launch
            \end{minted}

Replace inside \texttt{apm.launch}
\begin{verbatim}
<arg name="fcu_url" default="/dev/ttyACM0:57600" />
by
<arg name="fcu_url" default="udp://127.0.0.1:14551@14555" />
            \end{verbatim}

\begin{minted}{bash}
# Then launch
roslaunch apm.launch

# You can use rqt to interact with ArduPilot
rqt
            \end{minted}

\subsection{SITL + Gazebo + ROS}
The simulation is the tool to test the different code implemented to control the drones.
To do this, ROS has to be used in parallel to the SITL and Gazebo.

If the code implemented works in a simulation, it should also work in practice.

There are these two resources that could be useful to use ROS in parallel with Gazebo\cite{youtube_gazebo_ros} \cite{github_gazebo_ros}.



\section{Vicon and Kalman filter}
There are two ways to interface with Vicon. Either via Vicon DataStream SDK or VRPN.

\subsection{API}
\subsubsection{Vicon DataStream SDK}
It is a Development Kit from Vicon. It gives easy access to Vicon DataStream. It is compatible with Vicon Tracker and Nexus. It is the webpage \cite{vicon_sdk}. A ROS package has already been implemented to use it, vicon\_bridge \cite{github_vicon_bridge}.
The last commit is from 4 years ago, but it should still work according to this \cite{ros_packages_for_vicon}.

\subsubsection{VRPN}
It is a network-based interface to access data of motion capture software. It is compatible only with Vicon Tracker and not with Vicon Nexus. It works out of the box with vrpn\_client\_ros \cite{ros_vrpn_client_ros}. When an object is created in Vicon Tracker, the object information is stream automatically via vrpn.

\subsection{Implementation}
There is a project with Optitrack \cite{ardupilot_optitrack}. It explains how to pass the drone's position and attitude given by the Vicon system to the EKF of the drone, how to set up the EKF.

Recently, a project with Vicon on ArduPilot has to be done \cite{ardupilot_vicon}.

\section{Drone control}
To control the motor of the drone directly.

ArduPilot has a flight modes called \texttt{guided mode with no\_gps} \cite{ardupilot_flight_modes}.

A solution was proposed to control the speed of the motor \cite{github_ardupilot_11859}.
It consists of setting the right parameters and sending mavlink messages.
\texttt{SERVO<X>\_FUNCTION=RCIN<Y>PASSTHROUGH} and \texttt{RC\_CHANNELS\_OVERRIDE}.

Precaution has to be taken as it is particularly dangerous because of the risk of disconnection and latency that could cause the drone to go anywhere really fast.

